### 2010-12-28 Documentation/atropos/atropos.tex
ENH: dealt with all fixmes, grant support, afaik ready to be submitted modulo a 2nd reading
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@714 fd2da0a4-d968-48df-9cb5-d8c496287cbf

maximizes the posterior.  {\bf \textcolor{red}{ FIXME more specific?}}.

@@

%\gamma^{new}_k \leftarrow  \sum_i \frac{p^{old}_{ik}}{\sum_{j=1}^K p^{old}_{ij}}. 

@@

For parametric model update, for each of
  $K$ labels, we compute the mean,

@@

 \sigma^2_k \leftarrow  \frac{ \sum_{i=1}^N  (y_i - \mu_k ) p_k(l_k|y_i)}{ \sum_{i=1}^N p_k(l_k|y_i) }.

@@

 \boldsymbol{\Sigma}_{mn,k} \leftarrow \frac{ \sum_{i=1}^N  ( \mathbf{y}_i - \boldsymbol{\mu}_k ) p_k(l_k|\mathbf{y}_i)}{1 - \sum_{i=1}^N p^2_k(l_k|\mathbf{y}_i) }.

@@

A similar pattern is used in the multivariate and non-parametric cases.

@@

\subsection{Reproducibility of this Evaluation}
The brainweb data is freely available.  We used single-subject
brainweb data as is.  The 20 subject data, however, required excluding
non-cerebrum tissue classes.  The Hammers data was also used as is.
The scripts for the single-subject brainweb study is available in
supplementary material.  The initialization procedure for the brainweb 20 and
the Hammers evaluation data is based on freely available scripts
included with the ANTs toolkit, specifically  {\verb ants_multitemplate_labeling.sh } and  {\verb atroposBwebRF40FigureExample.sh }.

@@

\paragraph{Acknowledgments}
{This work was supported in part by NIH  {\bf {\textcolor{red}{ FIXME}}} }

>>>>

maximizes the posterior. 
% {\bf \textcolor{red}{ FIXME more specific?}}.

@@

@@

We update the parametric model parameters by computing, for each of
  $K$ labels, the mean,

@@

 \sigma^2_k \leftarrow  \frac{ \sum_{i=1}^N  (y_i - \mu_k )^T
   p_k(l_k|y_i) (y_i - \mu_k )}{ \sum_{i=1}^N p_k(l_k|y_i) }.

@@

 \boldsymbol{\Sigma}_{mn,k} \leftarrow \frac{ \sum_{i=1}^N  ( \mathbf{y}_i - \boldsymbol{\mu}_k )^T p_k(l_k|\mathbf{y}_i) ( \mathbf{y}_i - \boldsymbol{\mu}_k )}{1 - \sum_{i=1}^N p^2_k(l_k|\mathbf{y}_i) }.

@@

A similar pattern is used in non-parametric cases.

@@

\subsection{Reproducibility of this Evaluation}
The brainweb data is freely available.  We used single-subject
brainweb data as is but added a meta format data header to the raw
binary files.   An example copy of this header is contained in {\verb atroposBwebRF40FigureExample.sh }.  The 20 subject data, however, required excluding
non-cerebrum tissue classes.  The Hammers data was also used as is.
The scripts for the single-subject brainweb study is available in
supplementary material.  The initialization procedure for the brainweb 20 and
the Hammers evaluation data is based on freely available scripts
included with the ANTs toolkit, specifically  {\verb ants_multitemplate_labeling.sh } and  {\verb atroposBwebRF40FigureExample.sh }.

@@

\paragraph{Acknowledgments}
{This work was supported in part by NIH (AG17586, AG15116, NS44266, and
NS53488).}
